On the probability of finding a nonphysical solution through shadowing

### 2020-10-19 main.tex
Add grebogi citations

The existence of arbitrarily long shadowing solutions for sufficiently similar governing equations
has been proven for invertible hyperbolic maps by Anosov (1967) and Bowen (1970, 1978).
For non-hyperbolic systems, it is often possible to estimate the length of time for which shadowing
solutions exist. (Grebogi, Hammel, Yorke and Sauer (1990), Sauer, Grebogi and Yorke (1997)).

@@

\begin{figure}
    \centering
    \includegraphics[width=0.35\textwidth,height=2in]{figure/mapn0s0.png}
    \includegraphics[width=0.35\textwidth,height=2in]{figure/mapn5s0.1.png}
    \caption{Two chaotic maps (in red) and their associated stationary  distributions (in purple). The map on the right is only an \emph{infinitesimal} perturbation of that on the left; for more information see \cite{desmos}.}
    \label{fig:map}
\end{figure}
[Nisha: shadowing perturabtions predict tiny effects. Real effect is a lot more dramatic. Desmos plot.]
% give example of numerics that destroys physicalness
\bibliographystyle{spmpsci}
\bibliography{refs.bib}
\end{document}

>>>>

The existence of arbitrarily long shadowing solutions for sufficiently similar governing equations
has been proven for invertible hyperbolic maps by Anosov \cite{anosov} and Bowen \cite{bowen}.
For non-hyperbolic systems, it is often possible to estimate the length of time for which shadowing
solutions exist \cite{grebogi, hammel}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.35\textwidth,height=2in]{figure/mapn0s0.png}
    \includegraphics[width=0.35\textwidth,height=2in]{figure/mapn5s0.1.png}
    \caption{Two chaotic maps (in red) and their associated stationary  distributions (in purple). The map on the right is only an \emph{infinitesimal} perturbation of that on the left; for more information see \cite{desmos}.}
    \label{fig:map}
\end{figure}
[Nisha: shadowing perturabtions predict tiny effects. Real effect is a lot more dramatic. Desmos plot.]
% give example of numerics that destroys physicalness

\bibliographystyle{spmpsci}
\bibliography{refs.bib}
\include{supp}
\end{document}

### 2020-10-19 supp.tex
Add grebogi citations

\section{Supplementary material}
In this section, we discuss how to numerically compute the shadowing trajectories of the Lorenz map. One of the motivations for approximating the Lorenz map is that having a closed form expression is necessary in the algorithm we discuss for numerical shadowing solution computation. The program used to generate Figure 
\ref{fig:lorenz_map} is in

>>>>

\section{Supplementary material}
\subsection{The Lorenz Map}
\subsection{Approximation of the Lorenz Map}

\subsubsection{Computing shadowing solution of the Lorenz map}
In this section, we discuss how to numerically compute the shadowing trajectories of the Lorenz map. One of the motivations for approximating the Lorenz map is that having a closed form expression is necessary in the algorithm we discuss for numerical shadowing solution computation. The program used to generate Figure 
\ref{fig:lorenz_params_scaled} is in \verb+lorenz_map/shadow.py+. The main logic behind the numerical procedure to compute the shadowing solution can be found in that script, within the function \verb+shadow+, which calls \verb+find2+.
